Papers

### 2025-01-27 papers.qmd
fix typos and add in press heading

@@

- St. Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown D.M.Y., & Carter, MJ. (2025). Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00426-024-02059-z){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_st-germain-etal_autonomy-supportive-instructional-language-does-not-enhance-skill-acquisition-compared-to-controlling-instructional-language.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/expt_instructional-language){target="_blank" style="color: inherit;"}

@@

- Roth AM., Buggeln JH., Hoh JE., Wood JM., Sullivan SR., Ngo TT., Calalo JA., Lokesh R., Morton SM., Grill S., Jeka JJ., Carter MJ., & Cashaback JGA. (2024). Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson’s disease *PLoS Computational Biology*. ---
[{{< ai doi >}}](https://doi.org/10.1371/journal.pcbi.1012474){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_roth-etal_roles-and-interplay-of-reinforcement-based-and-error-based-processes-during-reaching-and-gait-in-neurotypical-adults-and-indi.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/CashabackLab/Roles_and_Interplay_of_Reinforcement_and_Error){target="_blank" style="color: inherit;"}

@@

- Ste-Marie DM., Carter MJ., & Yantha ZD. (2020). Self-controlled learning: Current findings, theoretical perspectives, and future directions. In N.J. Hodges & A.M. Williams (Eds.), *Skill Acquisition in Sport: Research, theory, and practice* (3rd ed.). Routledge. ---
[{{< ai doi >}}](https://doi.org/10.4324/9781351189750-7){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2019_ste-marie-etal_self-controlled-learning.pdf){target="_blank" style="color: inherit;"}

>>>>

## In Press

@@

- St. Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown DMY., & Carter, MJ. (2025). Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00426-024-02059-z){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_st-germain-etal_autonomy-supportive-instructional-language-does-not-enhance-skill-acquisition-compared-to-controlling-instructional-language.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/expt_instructional-language){target="_blank" style="color: inherit;"}

@@

- Roth AM., Buggeln JH., Hoh JE., Wood JM., Sullivan SR., Ngo TT., Calalo JA., Lokesh R., Morton SM., Grill S., Jeka JJ., Carter MJ., & Cashaback JGA. (2024). Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson’s disease. *PLoS Computational Biology*. ---
[{{< ai doi >}}](https://doi.org/10.1371/journal.pcbi.1012474){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_roth-etal_roles-and-interplay-of-reinforcement-based-and-error-based-processes-during-reaching-and-gait-in-neurotypical-adults-and-indi.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/CashabackLab/Roles_and_Interplay_of_Reinforcement_and_Error){target="_blank" style="color: inherit;"}

@@

- Ste-Marie DM., Carter MJ., & Yantha ZD. (2019). Self-controlled learning: Current findings, theoretical perspectives, and future directions. In N.J. Hodges & A.M. Williams (Eds.), *Skill Acquisition in Sport: Research, theory, and practice* (3rd ed.). Routledge. ---
[{{< ai doi >}}](https://doi.org/10.4324/9781351189750-7){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2019_ste-marie-etal_self-controlled-learning.pdf){target="_blank" style="color: inherit;"}
